A Data-Driven Approach to Power Converter Control via Convex Optimization

### 2017-02-27 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft_2/Draft_2.tex
updated files

\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters via Convex Optimization} 
% Title, preferably not more than 10 words.

@@

\begin{abstract}                % Abstract of not more than 250 words.
A new loop-shaping data-driven approach is presented for synthesizing controllers for the CERN power converter control system. This method uses the frequency response function (FRF) of a system in order to avoid the problem of unmodeled dynamics associated with parametric models. For this particular application, it is shown that a convex optimization problem can be formulated (in either the $H_\infty$ or $H_2$ sense) to shape the closed-loop FRF while guaranteeing the closed-loop stability. This optimization problem is realized by linearizing a non-convex constraint around a stabilizing operating point. The effectiveness of the method is illustrated by designing a controller for the SATURN power converter which is used in the Large Hadron Collider, in injector machines, and for pulsed applications at CERN. Experimental validation in the frequency-domain is also presented. 
\end{abstract}

%===============================================================================
\section{Introduction}
Today's industrial processes pose challenging problems to control engineers due to the increasing complexities of system structures. In order to simplify the controller design process, these systems are approximated with low-order models; this reduces both time and effort in synthesizing a controller. However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty. Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant). A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement uncertainty.

Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data. Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.  The widely used PID controller are usually tuned based on a set of time-domain or frequency-domain data.

Frequency-domain based controller synthesis methods are design schemes that continue to spark the interest of many researchers. The authors in \cite{KNND13b} establish a robust frequency-domain controller design method that requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping method for fixed-structure controllers is proposed in \cite{KNND13c}; however, stability is not guaranteed with this method and must be verified a posteriori. Controller synthesis methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. A convex optimization approach is used to design linearly-parameterized (LP) controllers with loop shaping and $\mathcal{H}_{\infty}$ performance in \cite{KG10}. This method is extended to multiple-input multiple-output (MIMO) systems for computing decoupling LP-MIMO controllers in \cite{GKL10b}. In \cite{NK14}, this method of designing LP controllers was further extended to MIMO systems with delay. Recently, the necessary and sufficient conditions for the existence of $\mathcal{H}_{\infty}$ controllers for SISO systems represented by their frequency response has been proposed in \cite{KNZ16}.

The method proposed in this paper invokes a new data-driven control design scheme for specific power converter applications at CERN. Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry). In fact, the authors in \cite{NW95} assert that even small deformations in the beam pipe can drastically change the impedance of the system and create stability issues. Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.  In this work, it is shown that a loop-shaping design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions). Additionally, with certain trivial conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.

The paper is organized as follows. The class of models represented by FRF's are addressed in section \ref{sec:prelim}. Section \ref{sec:system} discusses the framework of the power converter control system and its functionality at CERN. The main results and theoretical bases are addressed in section \ref{sec:main}; in this section, loop-shaping constraints are formulated for the power converter control system. Section \ref{sec:case} is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement. Finally, the concluding remarks are given in section \ref{sec:conclusion}.

\section{Preliminaries}
\label{sec:prelim}
The class of systems discussed in this paper will be Linear Time-Invariant Single-Input Single-Output (LTI-SISO) systems that will be represented by a FRF $G\jo$.  The FRF can be obtained directly with a given transfer function (TF) model, or through an identification experiment using the Fourier analysis method. Let $U\jo$ and $Y\jo$ represent the FRF's of the system input and output signals, respectively. Then the FRF of the system can be represented as 
\begin{equation}
G\jo = Y\jo U^{-1}\jo
\end{equation}
If the data is noisy, then $G\jo$ is characterized as the Empirical Transfer Function Estimate (ETFE) and is asymptotically unbiased \cite{Lju99}. For such systems, a multiplicative uncertainty can be considered to ensure robustness in the presence of noise perturbations. In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
\begin{equation}
\mathcal{G} = \{G_l\jo; \quad l=1,\ldots,p; \quad \forall \omega \in \Omega\}
\end{equation} 
$\Omega \in [0,\infty)$. For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted. However, in general, the design procedures outlined in this paper can be applied to the multi-model case (as will be seen in the case study).

@@

\section{System Framework}
\label{sec:system}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/circuit_partial_a}
\caption{Power converter filter schematic (from $v_i$ to $v_0$). The magnet represents the load of the process.}
\label{fig:circuit}
\end{figure}
The power converter voltage source filter has the structure shown in Fig.~\ref{fig:circuit}. The input voltage $v_i$ is the output of a pulse-width modulated system (which will be discussed in more detail in section \ref{sec:case}). The TF from $v_i$ to $v_0$ describes the output filter of the power converter. The magnet (i.e., the load) is connected to the output of the converter. For general applications at CERN, the objective is to control the current in the magnet (through $L_m$) such that the error between this output current and a delayed version of the reference current is minimized. However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$. This intermediate control is performed due to the fact that the output typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop. These large resonances are present because the values of the filter resistances are small (in order to reduce the power losses). Large resistance values can attenuate the resonances at the price of larger power losses. Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.

The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
\caption{Interconnection of the power converter control system. }
\label{fig:damping_loop}
\end{figure}
$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$). From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$ (where $H$ possesses a zero at zero). The objective of this application is to design controllers such the TFs from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
G(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
\end{aligned}
\end{equation}
where $k = [k_i,k_u,k_{m_1},k_{m_2}]$. Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$. These closed-loop TFs can easily be derived as follows:

\begin{align}
T^{\prime}(s,k) &= \frac{G(s)(1+k_u)}{1+G(s)[H_1(s,k)+H_2(s,k)]} \label{eq:Tclp}  \\ 
T(s,k) &= \frac{G(s)[1+k_u+C_m(s,k)]}{1+G(s)[H_1(s,k)+H_2(s,k)+C_m(s,k)]}  \label{eq:Tcl} 
\end{align}

For the remaining theoretical portions of this document, the loop-shaping technique will only be shown for $T(s,k)$, since the same procedures can also be applied to $T^{\prime}(s,k)$. Additionally, for notation purposes, the dependency in $s$ will be omitted and reiterated when deemed necessary. Additionally, all functions discussed hereafter will be FRF's with $s = j\omega$. For example, the denotation $T(k)$ represents $T(j\omega,k)$.

@@

\subsection{Convex Approximation}
The type of optimization problem that will be considered will have the following form:

\begin{equation} \label{eq:con_cav}
\begin{aligned}
& \underset{ x }{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & y(x)-z(x) < \gamma 
\end{aligned}
\end{equation}
where $y(x)$ and $z(x)$ are both convex functions of $x$ and $\{ \gamma \in \mathbb{R} : \gamma > 0\}$. This type of problem is convex-concave (due to the $-z(x)$ term); one solution to convexify this problem is to linearize $z(x)$ around an operating point $x_0$ and obtain the following optimization problem:

\begin{equation} \label{eq:con_lin}
\begin{aligned}
& \underset{ x }{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & y(x)-\bigl[ \nabla z(x_0) \bigr]^{\top} (x-x_0) < \gamma 
\end{aligned}
\end{equation}
where $\nabla z(x_0)$ is the gradient of $z(x)$ evaluated at $x_0$.

The control methodology is based on minimizing a control objective in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense. In subsequent sections, it will be shown that these performance constraints will have the following quadratic form:

\begin{equation} \label{eq:basic_ineq}
y^{\star}(x) \gamma^{-1} y(x) - z^{\star}(x)z(x) < 0 
\end{equation} 
where $y(x)$ and $z(x)$ are complex affine functions of the decision variable $x$ and $(\cdot)^{\star}$ denotes the complex conjugate of the argument. Let $f(x) = z^{\star}(x)z(x)$ with $z(x)$ defined as
$$z(x) = a_0 + a_1x_1 + a_2x_2 + ,\ldots , + a_nx_n$$
where $z:\mathbb{R}^n \rightarrow \mathbb{C}$ and $f:\mathbb{R}^n \rightarrow \mathbb{R}$. A first order Taylor series of $f(x)$ around an operating point $x_0$ can be formulated as follows:

\begin{equation} \label{eq:lin_fx}
f(x) \approx f(x_0) + D_f(x_0)[x-x_0]
\end{equation}
where
$$D_f(x_0) = \left[ \frac{\partial f(x)}{x_1}\Bigr|_{x=x_0}, \frac{\partial f(x)}{x_2}\Bigr|_{x=x_0},\ldots, \frac{\partial f(x)}{x_n}\Bigr|_{x=x_0}\right]$$

Without loss of generality, it can be shown that the left-hand side of (\ref{eq:lin_fx}) will always be greater than or equal to the right-hand side, i.e.,

\begin{equation} \label{eq:lin_inequality}
z^{\star}(x)z(x) \geq z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0
\end{equation}

where $z_0 = z(x_0)$. The condition in (\ref{eq:lin_inequality}) can easily be established by realizing the following inequality:

\begin{equation}
[z(x)-z_0]^{\star}[z(x)-z_0] \geq 0
\end{equation}

With this linearization, a sufficient condition for the inequality in (\ref{eq:basic_ineq}) can be developed as follows:

\begin{equation}
y^{\star}(x) \gamma^{-1} y(x) - [z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0]< 0 
\end{equation}

By using the Shur Complement Lemma \cite{BEN09}, the above condition can be expressed in terms of a Linear-Matrix-Inequality (LMI):

\begin{equation} \label{eq:LMI_1}
\begin{bmatrix}
z^{\star}(x)z_0 + z(x)z_0^{\star} - z_0^{\star}z_0 & \phantom{xx} y^{\star}(x) \\
y(x) & \phantom{xx} \gamma
\end{bmatrix}
\succ 0
\end{equation}

This type of formulation will be used in section \ref{sec:loop_shape} in order to construct a loop-shaping constraint on the closed-loop FRF.

\subsection{Control Performance}
Since the control methods discussed in this paper are based on the $\mathcal{H}_\lambda$ criterion ($\lambda \in \{2,\infty \}$), it is appropriate to first define this criterion in the context of this work. A typical control objective is to design a controller such that the following constraint is satisfied:
\begin{equation} \label{eq:WS_lt1}
\| W \mathcal{S}\| < 1
\end{equation}
where $\mathcal{S}$ is the sensitivity function of interest, and $W$ is a stable weighting function such that $\| W \mathcal{S}\|$ is bounded. The norm considered in (\ref{eq:WS_lt1}) can be either the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norm.

For SISO systems, and for a stable system $X(s)$, the $\mathcal{H}_2$ and $\mathcal{H}_\infty$ norms are defined as follows:
\begin{align*}
\| X\|_2^2 & := \frac{1}{2\pi} \int_{- \infty}^\infty |X(j\omega)|^2 d\omega \\
\| X\|_\infty & :=  \sup_{\omega} |X(j\omega)|
\end{align*}
It is imperative to note that the boundedness of spectral norm $X$ does not guarantee the stability of $X$.

A loop-shaping criterion can also be considered as a form of control performance. If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.  The next section will discuss how such an optimization problem can be formulated for this type of control methodology.

\subsection{Loop-Shaping Design}
\label{sec:loop_shape}
As asserted in section \ref{sec:system}, the objective of this control problem is to shape the FRF of $T(k)$. Suppose that a desired loop-shape is specified as $T_d$; the objective is to design the controllers in $k$ such that the closed-loop system $T(k)$ coincides with $T_d$ in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense. In the $\mathcal{H}_\infty$ sense, the objective is to minimize $ \|T(k) - T_d \|_\infty$; an equivalent representation of this objective is to minimize $\gamma$ such that $ \|T(k) - T_d \|_\infty < \gamma$. This criterion is satisfied if the the following optimization problem is considered:

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let us now define the following quantities:
\begin{equation} 
\begin{aligned}
w(k) &= G[1+k_u+C_m(k)] \\
z(k) &= 1+G[H_1(k)+H_2(k)+C_m(k)]
\end{aligned}
\end{equation}
where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:

\begin{equation}
\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
\end{equation}

>>>>

\title{A Data-Driven Approach to Power Converter Control via Convex Optimization} 
% Title, preferably not more than 10 words.

@@

\begin{abstract}                % Abstract of not more than 250 words.
A new model reference data-driven approach is presented for synthesizing controllers for the CERN power converter control system. This method uses the frequency response function (FRF) of a system in order to avoid the problem of unmodeled dynamics associated with low-order parametric models. For this particular application, it is shown that a convex optimization problem can be formulated (in either the $H_\infty$ or $H_2$ sense) to shape the closed-loop FRF while guaranteeing the closed-loop stability. This optimization problem is realized by linearizing a non-convex constraint around a stabilizing operating point. The effectiveness of the method is illustrated by designing a controller for the SATURN power converter which is used in the Large Hadron Collider, in injector machines, and for pulsed applications at CERN. Experimental validation in the frequency-domain is also presented. 
\end{abstract}

%===============================================================================
\section{Introduction}
Today's industrial processes pose challenging problems to control engineers due to the increasing complexities of system structures. In order to simplify the controller design process, these systems are approximated with low-order parameteric models; this reduces both time and effort in synthesizing a controller. However, this approximation can create stability and performance problems since these low-order models are subject to model uncertainty. Data-driven control methods seek to alleviate this problem by synthesizing controllers based on time-domain or frequency-domain data (i.e., synthesis is model independant). A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{FK13a}; the authors assert that model-based control methods are inherently less robust due to the unmodeled dynamics of a process, and that these controllers are unsafe for practical applications. In other words, the parametric uncertainties and the unmodeled dynamics associated with the data-driven scheme are irrelevant, and the only source of uncertainty is the measurement error.

%Data-driven controllers can be synthesized either on-line or off-line; the on-line methods such as the classical direct adaptive control (MRAC) \cite{LLMK11}, model-free adaptive control (MFAC) \cite{HJ13}, and the unfalsified control (UC) \cite{ST97} methodologies design controllers using time-domain data. Iterative feedback tuning (IFT) \cite{Hja02}, correlation-based tuning (CBT) \cite{KMB02a}, virtual reference feedback tuning (VRFT) \cite{CLS02}, non-iterative data-driven model reference control \cite{KVB07} methodologies are all off-line time-domain data-driven methods.  The widely used PID controller are usually tuned based on a set of time-domain or frequency-domain data.

Frequency-domain based controller synthesis methods are design schemes that continue to spark the interest of many researchers. The authors in \cite{KNND13b} establish a robust frequency-domain controller design method that requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping method for fixed-structure controllers is proposed in \cite{KNND13c}; however, stability is not guaranteed with this method and must be verified a posteriori. Controller synthesis methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. A convex optimization approach is used to design linearly-parameterized (LP) controllers with loop-shaping and $\mathcal{H}_{\infty}$ performance in \cite{KG10}. The constraints are convexified around a desired open-loop transfer function. A frequency-domain approach for computing low-order multivariable LP controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. Moreover, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which leads to the same constraints as \cite{KG10} for PID controllers. This method is then generalized to MIMO PID controller design in \cite{BHA16} for stable systems. More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{KK16}. This method is not limited to LP controllers and stable systems and can consider $H_2$ performance as well. Recently, the necessary and sufficient conditions for the existence of $\mathcal{H}_{\infty}$ controllers for SISO systems represented by their frequency response has been proposed in \cite{KNZ16}. The advantage of this method is that it does not require an initial stabilizing controller and converges to the global optimal solution if the controller order goes to infinity.

The method proposed in this paper is an extension of \cite{KK16} to the model reference control problem and invokes a new data-driven control design scheme for specific power converter applications at CERN. Currently, the load (i.e., the magnet of the particle accelerator) is approximated as a simple first-order system (series $RL$ circuit); however, it has been shown in \cite{KZ98}, \cite{NW95} and \cite{NS79} that the vacuum chamber of the magnet is also frequency dependent (mainly due to the coupling effects of the beam and deformations in the chamber geometry). In fact, the authors in \cite{NW95} assert that even small deformations in the beam pipe can drastically change the impedance of the system and create stability issues. Therefore, it is appropriate to consider a data-driven based design to regulate the power converter control system.  In this work, it is shown that a model reference design in the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ sense can be formulated through a convex optimization problem; however, the methods described in this paper can also be applied to mixed $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems (i.e., minimizing the norm of weighted sensitivity functions). Additionally, with certain trivial conditions on the controller parameters, it is shown that the closed-loop stability is guaranteed.

The paper is organized as follows. The class of models represented by FRF's are addressed in Section \ref{sec:prelim}. Section \ref{sec:system} discusses the framework of the power converter control system and its functionality at CERN. The main results and theoretical bases are addressed in Section \ref{sec:main}; in this section, loop-shaping constraints are formulated for the power converter control system. Section \ref{sec:case} is dedicated to a case study where the effectiveness of the method is demonstrated by applying the proposed design scheme to a power converter control system for a specific accelerator requirement. Finally, the concluding remarks are given in section \ref{sec:conclusion}.

\section{Preliminaries}
\label{sec:prelim}
The class of systems discussed in this paper will be Linear Time-Invariant Single-Input Single-Output (LTI-SISO) systems that will be represented by a FRF $G\jo$.  The FRF can be obtained directly with a given transfer function (TF) model, or through an identification experiment using the Fourier analysis method. Let $U\jo$ and $Y\jo$ represent the FRFs of the system input and output signals, respectively. Then the FRF of the system can be represented as 
\begin{equation}
G\jo = Y\jo U^{-1}\jo
\end{equation}
In general, a set $\mathcal{G}$ can be formulated to represent a plant model containing $p$ FRF models:
\begin{equation}
\mathcal{G} = \{G_l\jo; \quad l=1,\ldots,p; \quad \forall \omega \in \Omega\}
\end{equation} 
$\Omega \in [0,\infty)$. For simplicity, one model from the set $\mathcal{G}$ will be considered, and the subscript $l$ will be omitted. However, in general, the design procedures outlined in this paper can be applied to the multi-model case (as will be seen in the case study).

@@

\begin{remark}
In this work, the control structure will contain both discrete-time and continuous time systems. However, the proposed method synthesizes controllers based on the FRF of the system (i.e., the design method is not based on the parametric model); therefore, if the Nyquist-Shannon sampling rate is met, then the FRF of discrete-time systems will be nearly identical to that of the continuous-time system.
\end{remark}

\section{System Framework}
\label{sec:system}
\begin{figure*}
\centering
\includegraphics[width=1.7\columnwidth]{../pics/voltage_loop_schematic_color_coded}
\caption{Power converter control system schematic. The magnet represents the load of the process while the DSP implements the control strategy. The blue portion represents the power electronics of the converter; the yellow portion represents the analog process of the converter with the load; the red portion represents the digital-signal processor (DSP) which implements the control strategy; and the green block represents the measurement board which reads the desired control variables and sends the information to the DSP for processing.}
\label{fig:circuit}
\end{figure*}
A schematic of the power converter control system is shown in Fig.~\ref{fig:circuit}. Specific portions of the schematic are color-coded in order to construct the associated block diagram. Note that there are two power converter branches assembled in series in this schematic; however, both branches possess the same components with identical values. Therefore, the analysis and control strategy can be performed in one branch and then scale the controller parameters accordingly (i.e., by a factor of 2). The input voltage for one of the high frequency (HF) filters will be denoted as $v_i$ while the output voltage of the filter (for one branch) will be denoted as $v_0$. The TF from $v_i$ to $v_0$ describes the output filter of the power converter for one branch. For general applications at CERN, the objective is to control the current in the magnet such that the error between this output current and a delayed version of the reference current is minimized. However, the objective of this paper is to design and implement a controller to shape the FRF between the reference voltage and $v_0$. This intermediate control is performed due to the fact that the output typically possesses large resonances, and a controller is required to attenuate these resonances in order to ensure better performance in the current loop. These large resonances are present because the values of the filter resistances are small (in order to reduce the power losses). Large resistance values can attenuate the resonances at the price of larger power losses. Another reason for implementing this type of control structure at CERN is for commissioning purposes; if/when faults occur in the system, each loop can be verified one at a time to ensure quality operation.

The block diagram of the control strategy is shown in Fig.~\ref{fig:damping_loop}. This block diagram is color-coded to correlate with the structure of the schematic in Fig.~\ref{fig:circuit}. The analog-to-digital converter (ADC) is used to process the information from the analog system to the DSP; $G_0(s)$ represents the TF from $v_i$ to $v_0$; $H(s)$ represents the TF from $v_0$ to $i_c$ (the current through the capacitor in the HF filter); $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay that is used to approximate the dynamics of the power electronics; and $C(s)$ is a PI controller, i.e., $$C(z^{-1}) = k_{p_1} + k_{p_2}\frac{t_s z^{-1}}{1-z^{-1}}$$ where $t_s \: [s]$ is the sampling rate of the DSP. The ADCs have very fast dynamics relative to the other subsystems in the loop; for this reason, it is appropriate to consider the ADCs as pure time delays (which will be denoted with a delay $\tau_{a} \: [s]$). The transfer function analyzer (TFA) is used for identification purposes, and will be discussed in the case study. As stated in the Remark in the previous section, the FRFs of continuous-time and discrete-time systems are nearly identical when the Nyquist-Shannon sampling theorem is met. Since the proposed method invokes a data-driven method using the FRF of a system, all functions discussed hereafter will be FRFs.

From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$ (where $H$ possesses a zero at zero). The objective of this application is to design controller's gains such that the FRFs from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired reference models.
\begin{figure*}
\centering
\includegraphics[width=1.6\columnwidth]{../pics/voltage_loop_color_coded}
\caption{Interconnection of the power converter control system. During normal operation, the TFA along with the connections indicated with a dashed-black line are not present.}
\label{fig:damping_loop}
\end{figure*}

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(k) &:= k_iP_1H;  &H_2(k) &:= k_uP_2e^{-j\omega \tau_{a}} \\
G &:= G_0e^{-j\omega\tau}; &C_m(k) &:= k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}\\ 
\end{aligned}
\end{equation}
where $k = [k_i,k_u,k_{m_1},k_{m_2}]$. Let the FRF from $v_d$ to $v_0$ be denoted as $T^{\prime}(k)$ and the FRF from $v_r$ to $v_0$ be denoted as $T(k)$. These closed-loop FRFs can easily be derived as follows:

\begin{align}
T^{\prime}(k) &= \frac{G(1+k_u)}{1+G[H_1(k)+H_2(k)]} \label{eq:Tclp}  \\ 
T(k) &= \frac{G[1+k_u+C_m(k)]}{1+G[H_1(k)+H_2(k)+e^{-\tau_{a}s} P_2C_m(k)]}  \label{eq:Tcl} 
\end{align}

For the remaining theoretical portions of this document, the model reference control will only be shown for $T(k)$, since the same procedures can also be applied to $T^{\prime}(k)$.

@@

\subsection{Convex Approximation}
In subsequent sections, it will be shown that the type of optimization problem that will be considered will have the following form:

\begin{equation} \label{eq:con_cav}
\begin{aligned}
& \underset{ k }{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & y^{\star}(k) \gamma^{-1} y(k) - z^{\star}(k)z(k) < 0 
\end{aligned}
\end{equation}
where $y(k)$ and $z(k)$ are linear functions of the decision variable $k$ and $(\cdot)^{\star}$ denotes the complex conjugate of the argument. This type of problem is convex-concave (due to the $-z^{\star}(k)z(k)$ term). To convexify this constraint, the term $z^{\star}(k)z(k)$ can be linearized around an operating point $k_0$; without loss of generality, it can be shown that the linearization of $z^{\star}(k)z(k)$ leads to the following constraint:

\begin{equation} \label{eq:lin_inequality}
z^{\star}(k)z(k) \geq z^{\star}(k)z_0 + z(k)z_0^{\star} - z_0^{\star}z_0
\end{equation} 
where $z_0 = z(k_0)$. The condition in (\ref{eq:lin_inequality}) can easily be established by realizing the following inequality:

\begin{equation}
[z(k)-z_0]^{\star}[z(k)-z_0] \geq 0
\end{equation}
With this linearization, a sufficient condition for the inequality in (\ref{eq:con_cav}) can be developed as follows:

\begin{equation}
y^{\star}(k) \gamma^{-1} y(k) - [z^{\star}(k)z_0 + z(k)z_0^{\star} - z_0^{\star}z_0]< 0 
\end{equation}
By using the Shur Complement Lemma \cite{BEN09}, the above condition can be expressed in terms of a Linear-Matrix-Inequality (LMI):

\begin{equation} \label{eq:LMI_1}
\begin{bmatrix}
z^{\star}(k)z_0 + z(k)z_0^{\star} - z_0^{\star}z_0 & \phantom{kk} y^{\star}(k) \\
y(k) & \phantom{kk} \gamma
\end{bmatrix}
\succ 0
\end{equation}
This type of formulation will be used in the next section in order to construct a model reference control objective.

\subsection{Control Performance}  \label{sec:controlperformance}
For SISO systems, and for a stable system $X(s)$, the $\mathcal{H}_2$ and $\mathcal{H}_\infty$ norms are defined as follows:
\begin{align*}
\| X\|_2^2 & := \frac{1}{2\pi} \int_{- \infty}^\infty |X(j\omega)|^2 d\omega \\
\| X\|_\infty & :=  \sup_{\omega} |X(j\omega)|
\end{align*}
It is imperative to note that the boundedness of spectral norm $X$ does not guarantee the stability of $X$.

A model reference criterion can be considered as a form of control performance. If $T$ is the closed-loop FRF and $T_d$ is the desired FRF, then one can consider minimizing $(T-T_d)$ in either the $\mathcal{H}_2$ or $\mathcal{H}_\infty$ sense in order to shape $T$.

In the $\mathcal{H}_\infty$ sense, the objective is to minimize $ \|T(k) - T_d \|_\infty$; an equivalent representation of this objective is to minimize $\gamma$ such that $ \|T(k) - T_d \|_\infty < \gamma$. This criterion is satisfied if the following optimization problem is considered:

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let us now define the following quantities:
\begin{equation} 
\begin{aligned}
w(k) &= G[1+k_u+C_m(k)] \\
z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)]
\end{aligned}
\end{equation}
where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:
$$
\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
$$

Note that this constraint has the exact form as in (\ref{eq:con_cav}); therefore, the convex constraint in (\ref{eq:LMI_1}) can be utilized to construct the model-reference optimization problem as follows:
\begin{equation} \label{eq:loop_shape_LMI_inf}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \gamma  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
w(k)-z(k)T_d & \phantom{xx}\gamma
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$, where $$z_0 = 1+G[H_1(k_0) + H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]$$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.

In a similar manner, the following convex optimization problem can be considered for minimizing  $ \|T(k)- T_d \|_2^2$, as follows:
\begin{equation} \label{eq:loop_shape_LMI_2}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \int_0^\infty \gamma(\omega) d\omega  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
w(k)-z(k)T_d & \phantom{xx}\gamma(\omega)
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. For this $\mathcal{H}_2$ problem, note that $\gamma$ is now a function of $\omega$ (which contrasts with the optimization problem in the $\mathcal{H}_\infty$ sense).
